### 2016-01-18 papers/CAFe/HIPS-paper/conclusions.tex
edits

However significant challenges arise as hardware adapts to the end of Moore's
Law\cite{exascale:workshop:2011}.  The revolution occurring in hardware architecture
has completely altered the landscape for scientific computing as a code designed for
distributed memory bulk synchronous model of parallelism may actually run slower on
advanced hardware\cite{Dubey:2014:SSC:2686745.2686756}.

@@

Tools to automatically convert existing applications to run under the OCR model faces challenges.  For
example, the hundreds of MPI functions would have to be semantically understood by the tools,
integrated with existing OpenACC directives (for example), a DAG generated for the complete
program, and then transformed into an OCR program.

>>>>

However, significant challenges arise as hardware adapts to the end of Moore's
Law\cite{exascale:workshop:2011}.  The revolution occurring in hardware architecture
has completely altered the landscape for scientific computing as a code designed for the
distributed memory bulk synchronous model of parallelism may actually run slower on
advanced hardware\cite{Dubey:2014:SSC:2686745.2686756}.

@@

%%%
%%% MJS: I cut the following out - conversion of MPI -> OCR is not in scope for us, and 
%%% we don't want to argue one way or the other about that topic.  Stay focused on CAF/CAFe.
%%%
%Tools to automatically convert existing applications to run under the OCR model faces challenges.  For
%example, the hundreds of MPI functions would have to be semantically understood by the tools,
%integrated with existing OpenACC directives (for example), a DAG generated for the complete
%program, and then transformed into an OCR program.
